---
title: "Respirometry BE"
editor_options: null
  chunk_output_type: console
output:
  html_document:
    df_print: paged
chunk_output_type: console
---
### Goal: Rear UZ and BE at 23C at 16:8 and 12:12 L:D regimens (UZ12, UZ16, BE12, BE16). Track CO2 production as a function of number of days after molting into the 5th instar. Track average weight gain as a function of number of days after molting into the 5th instar. Compare CO2 production and weight gain within strain and between L:D then compare L:D between strains 

#Libraries and Reading in Data
````{r}
#############--------------Read in the data-----------------######################
#PC
setwd("/Users/jbrown/Documents/GitHub/Respirometry/Data/")
data=read_excel("Respir.xlsx")
##Remove rows with NA
data=subset(data, VCO2!="NA")

#MAC
#data=read_excel("/Users/JamesB/Google Drive/Graduate School/Self_JamesTBrown/GitHub/Respirometry/Data/Respir.xlsx", sheet = "Sheet1")
##Remove rows with NA
data=subset(data, VCO2!="NA")

#############--------------Preping Data-----------------######################
#Removing "Blank Control" syringes
data=subset(data,data$syringe!="Blank Control")
##Set "syringe" identifier as a character
data$syringe=as.character(data$syringe)
##Set "treat" (read:treatment) as a factor (read:independent variable)
data$treat=as.factor(data$treat)
##This code breaks apart the data in the column "treat" into "strain" and "photoperiod"
data$strain<-as.factor(data$strain)
data$treat<-as.factor(data$treat)
str(data)



#############--------df for Larvae Plots and Data Analysis---------#############
dataBE=data
dataBE=subset(dataBE, strain=="BE")
dataBE=subset(dataBE, stage=="L")
dataBE=subset(dataBE, treat=="1" | treat=="2")
dataBE=subset(dataBE, Tray=="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")
par(mfrow=c(1,1))

#############------df for Larvae Freq Plots and Data Analysis-------#############
dataFREQm=data
dataFREQm=subset(dataFREQm,strain!="UZ")
dataFREQm=subset(dataFREQm,stage=="L")
dataFREQm=subset(dataFREQm,treat=="1" | treat=="2")
dataFREQm=subset(dataFREQm, Tray=="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")


#############------df for Pupae Freq Plots and Data Analysis-------#############
dataFREQp=data
dataFREQp=subset(dataFREQp, strain=="BE")
dataFREQp=subset(dataFREQp, stage=="P" & treat=="1" | treat=="2")

#############------df 1st 10 days Plots and Data Analysis-------#############
data1to10=dataBE
data1to10=subset(data1to10, day==1 | day==2 | day==3 | day==4 | day==5 | day==6 | day==7 | day==8 | day==9 | day==10)
mod=aov(data1to10$co2_hourly_mass~data1to10$treat)
data1to10$stdresd<-as.vector(scale(resid(mod)))
`````

#Plots of CO2 production over time df: dataBE
`````{r}
#INDIVIDUAL POINT PLOTS: Hourly CO2 production
ggplot(data=dataBE,aes(x=day,y=co2_hourly))+
  geom_point()+geom_line()+
  ggtitle("BE Larvae CO2 production")+
  ylab("CO2 production")+
  facet_wrap(~syringe)+
  scale_x_continuous(breaks = c(5,15,30,45,60))+
  scale_y_continuous(limits=c(0,8))

#INDIVIDUAL POINT PLOTS: Hourly CO2 production by mass
ggplot(data=dataBE,aes(x=day,y=co2_hourly_mass))+
  geom_point()+geom_line()+
  ggtitle("BE Strain weighted by Mass")+
  ylab("CO2 production by mass")+
  facet_wrap(~syringe)+
  scale_x_continuous(breaks = c(5,15,30,45,60))+
  scale_y_continuous(limits=c(0,100))

##BOXPLOT: Hourly CO2 production
ggplot(data=dataBE,aes(x=treat,y=co2_hourly, color=treat))+
  geom_boxplot()+stat_smooth(method="loess")+
  theme_classic()+
  ggtitle("BE Larvae CO2 production")+
  ylab("CO2 production")

##BOXPLOT: Hourly CO2 production by mass
ggplot(data=dataBE,aes(x=treat,y=co2_hourly_mass, color=treat))+
  geom_boxplot()+stat_smooth(method="loess")+
  theme_classic()+
  ggtitle("BE Larvae CO2 production by Mass")+
  ylab("CO2 production by mass")
`````

##Larvae and Pupae freqs df: dataFREQm, dataFREQp
```{r}
str(dataFREQm)
dataFREQm=subset(dataFREQm, treat=="2")
#Larva MASS: Chaqnge Over Time
ggplot(data=dataFREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe))+
  theme_classic()+
  ggtitle("BE Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13))+
  scale_y_continuous(limits=c(0,0.15))

ggplot(data=dataFREQm,aes(x=co2_hourly,y=mass))+
  geom_point()+stat_smooth(method="lm")+
  theme_classic()+
  ggtitle("BE Larvae Mass Increase")+
  ylab("Mass")+xlab("CO2 Production")+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(limits=c(0,0.20))

#Larva: Distribution between conditions
ggplot(dataFREQp, aes(day, fill = treat))+
  theme_classic()+
  geom_bar()+
  labs(title = "Number of Larvae across time", x = "Day", y = "Number of Individuals")+
  scale_x_continuous(breaks = c(0,1,5,10,20,40,60))+
  scale_y_continuous()

#PUPA: Distribution between conditions
ggplot(dataFREQp, aes(day, fill = treat))+
  theme_classic()+
  geom_bar()+
  labs(title = "Number of Pupae across time", x = "Day", y = "Number of Individuals")+
  scale_x_continuous(breaks = c(0,1,5,10,20,40,60))+
  scale_y_continuous()

#PUPA: Distribution across time
ggplot(dataFREQp, aes(day, fill = stage))+
  theme_classic()+
  geom_bar()+
  labs(title = "Larvae stage across time", x = "Day", y = "Number of Individuals")+
  scale_x_continuous(breaks = c(0,1,5,10,20,40,60))+
  scale_y_continuous()
```

##Plotting CO2 for the 1st 5 days df: data=dataa
````{r}
##Plotting CO2 production for the first 10 days 
ggplot(data1to10,aes(x=day,y=co2_hourly_mass,fill=treat))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(title="Day 1 thru 10 UZ Larvae",x ="Day", y = "Hourly CO2 Production by Mass")+
  scale_colour_discrete(name="Treatment",breaks=c("1","2"),labels=c("Diapause","Non-Diapause"))

ggplot(data1to5,aes(x=factor(day),y=stdresd))+
  geom_boxplot(aes(fill=treat))+
  scale_fill_discrete("",breaks=c("1","2"), labels=c("Diapause", "Non Diapause"))+
  labs(title="Day 1 thru 5 UZ Larvae",x ="Day", y = "Hourly CO2 Production by Mass")

##Mass Accumulation
ggplot(data1to5,aes(x=day,y=mass,color=treat))+
  geom_point()+
  geom_smooth(method="lm")+
  labs(title="Day 1 thru 5 UZ Larvae Mass Increase",x ="Day", y = "Mass")+
  scale_colour_discrete(name="Treatment", breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))
````

##Data Analysis
````{r}
## Significance of photoperiod and/or day to explain hourly CO2 production 
mod=aov(dataBE$co2_hourly ~ dataBE$treat*dataBE$day)
summary(mod)
par(mfrow=c(2,2))
plot(mod, main="BE Larvae")

## Significance of photoperiod and/or day to explain hourly CO2 production weighted by mass
mod1=aov(dataBE$co2_hourly_mass ~ dataBE$treat*dataBE$day)
summary(mod1)
par(mfrow=c(2,2))
plot(mod1, main="BE Larvae by Mass")

###########################Graph of Data###################################
##Line plot of each syringe CO2 production averages by treatment
gd=data1to10 %>% group_by(treat, day) %>% summarise(co2_hourly_mass = mean(co2_hourly_mass))

ggplot(day1to10,aes(x=day,y=co2_hourly_mass, color=treat))+
  theme_minimal()+
  geom_line(aes(group=syringe),alpha=0.3)+
  geom_line(data=gd, alpha=0.8,size=3)+
  labs(title ="Rep 1: BE larvae",x = "Day",y = "CO2 Production by Mass")+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"), labels=c("Diapause", "Non-Diapause"))

day1=subset(day1to10,day=="1")
mod1=lmer(co2_hourly_mass~treat*day+(day|syringe),data=day1)
summary(mod1)

day2=subset(day1to10, day<3)
mod2=lmer(co2_hourly_mass~treat*day+(day|syringe),data=day2)
summary(mod2)

day3=subset(day1to10, day<4)
mod3=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day3)
summary(mod3)

day4=subset(day1to10, day<5)
mod4=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day4)
summary(mod4)

day6=subset(day1to10, day<7)
mod6=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day6)
summary(mod6)

day7=subset(day1to10, day<8)
mod7=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day7)
summary(mod7)

day8=subset(day1to10, day<9)
mod8=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day8)
summary(mod8)

day9=subset(day1to10, day<7)
mod9=lmer(co2_hourly_mass~treat*day+(1|syringe),data=day9)
summary(mod9)

day10=subset(day1to10, day<10)
mod10=lmer(co2_hourly_mass~treat*day+(day|syringe),data=day10)
summary(mod10)
plot(mod10)
````