---
title: "Respirometry"
editor_options: null
chunk_output_type: inline
output: html_document
df_print: paged
---
### Goal: Rear UZ and BE at 23C at 16:8 and 12:12 L:D regimens (UZ12, UZ16, BE12, BE16). Track CO2 production as a function of number of days after molting into the 5th instar. Track average weight gain as a function of number of days after molting into the 5th instar. Compare CO2 production and weight gain within strain and between L:D then compare L:D between strains 

##Call Data
````{r}
library(splines)
library(stats)
library(readxl)
library(ggplot2)
library(nlme)
library(lme4)
library(lmerTest)
library(ez)
library(lsr)
library(dplyr)
library(tidyr)
library(MASS)
library(doBy)
library(plyr)
#############--------------Read in the data-----------------######################
#PC
setwd("/Users/jbrown/Documents/GitHub/Respirometry/Data/")
data=read_excel("Respir.xlsx")


#MAC
#data=read_excel("/Users/JamesB/Google Drive/Graduate School/Self_JamesTBrown/GitHub/Respirometry/Data/Respir.xlsx", sheet = "Sheet1")


##Remove rows with NA
data=subset(data, VCO2!="NA")
data=subset(data, syringe!="Blank Control")
str(data)
````

##Data Prep
````{r}
#######################################
##########Subsetting Data##############
#######################################
data=subset(data,data$syringe!="Blank Control") #Removing "Blank Control" syringes
data$syringe=as.character(data$syringe) #Set "syringe" identifier as a character
data$strain<-as.factor(data$strain) #set strain as ind var
data$treat<-as.factor(data$treat) #set treat as factor as ind var
str(data)

##########################################
#df BE Rep1 Stages Plots and Data Analysis
##########################################
dataBEr1s=data
dataBEr1s=subset(dataBEr1s, treat=="1" | treat=="2")
dataBEr1s=subset(dataBEr1s, Tray=="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")

##########################################
#df BE Rep2 Stages Plots and Data Analysis
##########################################
dataBEr2s=data
dataBEr2s=subset(dataBEr2s, treat=="1" | treat=="2")
dataBEr2s=subset(dataBEr2s, Tray=="16,23 0206" | Tray=="12,23 0208")

##########################################
#df UZ Rep1 Stages Plots and Data Analysis
##########################################
dataUZr1s=data
dataUZr1s=subset(dataUZr1s, treat=="1" | treat=="2")
dataUZr1s=subset(dataUZr1s, Tray=="16,23 1228" | Tray=="12,23 1228")

#######################################
##df BE Rep 1 Plots and Data Analysis##
#######################################
dataBEr1=data
dataBEr1=subset(dataBEr1, strain=="BE")
dataBEr1=subset(dataBEr1, stage=="L")
dataBEr1=subset(dataBEr1, treat=="1" | treat=="2")
dataBEr1=subset(dataBEr1, Tray=="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")

#######################################
##df BE Rep 2 Plots and Data Analysis##
#######################################
dataBEr2=data
dataBEr2=subset(dataBEr2, strain=="BE")
dataBEr2=subset(dataBEr2, stage=="L")
dataBEr2=subset(dataBEr2, treat=="1" | treat=="2")
dataBEr2=subset(dataBEr2, Tray=="16,23 0206" | Tray=="12,23 0208")

#######################################
##df UZ Rep 1 Plots and Data Analysis##
#######################################
dataUZr1=data
dataUZr1=subset(dataUZr1, strain=="UZ")
dataUZr1=subset(dataUZr1, stage=="L")
dataUZr1=subset(dataUZr1, treat=="1" | treat=="2")
dataUZr1=subset(dataUZr1, Tray=="16,23 1228" | Tray=="12,23 1228")
`````

##Larvae Change in Mass Over Time and Stage Plots
```{r}
dataBEr1p=dataBEr1
dataBEr1p=subset(dataBEr1, day<=12)
ggplot(data=dataBEr1p,aes(x=day,y=mass))+
  stat_smooth(method="loess")+
  facet_wrap(~syringe)+
  ylab("Mass")+xlab("Day")

dataBEr2p=dataBEr2
dataBEr2p=subset(dataBEr2p, day<=12)
ggplot(data=dataBEr2p,aes(x=day,y=mass))+
stat_smooth(method="loess")+
  facet_wrap(~syringe)+
  ylab("Mass")+xlab("Day")

dataUZr1p=dataUZr1
dataUZr1p=subset(dataUZr1p, day<=12)
ggplot(data=dataUZr1p,aes(x=day,y=mass))+
stat_smooth(method="loess")+  
  facet_wrap(~syringe)+
  ylab("Mass")+xlab("Day")
```

```{r}
##BE Rep 1##
dataBEr1FREQm=dataBEr1
dataBEr1FREQm=subset(dataBEr1FREQm, treat=="2")
#Larva MASS: Change Over Time
ggplot(data=dataBEr1FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  theme_classic()+
  ggtitle("BE Rep1 Non Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=3)+ geom_vline(xintercept=6)

##BE Rep 1##
dataBEr1FREQm=dataBEr1
dataBEr1FREQm=subset(dataBEr1FREQm, treat=="1")
dataBEr1FREQm=subset(dataBEr1FREQm, day<=20)
#Larva MASS: Change Over Time
ggplot(data=dataBEr1FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  ggtitle("BE Rep1 Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=4)+ geom_vline(xintercept=7)

##BE Rep 1##
dataBEr1s=subset(dataBEr1s,stage=="L"|stage=="P")
dataBEr1s=subset(dataBEr1s, treat=="2")
dataBEr1s=subset(dataBEr1s, day<=20)
#Stages: Change Over Time
ggplot(dataBEr1s, aes(x=day, fill=stage))+
  theme_classic()+
  geom_histogram(binwidth=.5, alpha=.5, position="identity")+
  scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,13,15,17))+
  ggtitle("BE Non Diapause Rep1 Stages")+
  ylab("# of Insects in each stage")+xlab("Day")
```

```{r}
##BE Rep 2 ##
dataBEr2FREQm=dataBEr2
dataBEr2FREQm=subset(dataBEr2FREQm, treat=="2")
#Larva MASS: Change Over Time
ggplot(data=dataBEr2FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  theme_classic()+
  ggtitle("BE Rep2 Non Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(1,3,4,5,6,8))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=2)+ geom_vline(xintercept=4)

##BE Rep 2 ##
dataBEr2FREQm=dataBEr2
dataBEr2FREQm=subset(dataBEr2FREQm, treat=="1")
dataBEr2FREQm=subset(dataBEr2FREQm, day<=20)
dataBEr2s=subset(dataBEr2s,stage=="L"|stage=="P")
#Larva MASS: Change Over Time
ggplot(data=dataBEr2FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  ggtitle("BE Rep2 Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=5)+ geom_vline(xintercept=8)

#Stages: Change Over Time
ggplot(dataBEr2s, aes(x=day, fill=stage, color=stage))+
  theme_classic()+
  geom_histogram(alpha=.3)+
  scale_x_discrete(limits=c(1,3,4,5,6,8,9,10))+
  ggtitle("BE Non Diapause Rep2 Stages")+
  ylab("# of Insects in each stage")+xlab("Day")


##UZ Rep 1##
dataUZr1FREQm=dataUZr1
dataUZr1FREQm=subset(dataUZr1FREQm, treat=="2")
#Larva MASS: Change Over Time
ggplot(data=dataUZr1FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  theme_classic()+
  ggtitle("UZ Rep1 Non Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(1,2,4,5,6,7,10,11,13,14,16,18,19))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=4)+ geom_vline(xintercept=6)
  
##UZ Rep 1##
dataUZr1FREQm=dataUZr1
dataUZr1FREQm=subset(dataUZr1FREQm, treat=="1")
dataUZr1FREQm=subset(dataUZr1FREQm, day<=20)
#Larva MASS: Chaqnge Over Time
ggplot(data=dataUZr1FREQm,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  geom_smooth()+
  theme_classic()+
  ggtitle("UZ Rep1 Diapause Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")+
  scale_x_continuous(breaks = c(1,2,4,5,6,7,10,11,13,14,16,18,19))+
  scale_y_continuous(limits=c(0,0.15))+ geom_vline(xintercept=4)+ geom_vline(xintercept=8)

##UZ Rep 1##
dataUZr1s=subset(dataUZr1s,stage!="E")
dataUZr1s=subset(dataUZr1s,stage!="Pre")
dataUZr1s=subset(dataUZr1s,stage!="I")
dataUZr1s=subset(dataUZr1s,stage!="A")
dataUZr1s=subset(dataUZr1s,treat=="2")
#Stages: Change Over Time
ggplot(dataUZr1s, aes(x=day, fill=stage))+
  theme_classic()+
  geom_histogram(binwidth=.5, alpha=.5, position="identity")+
  scale_x_discrete(limits=c(1,2,4,5,6,7,10,11,13,14,16,18,19))+
  ggtitle("UZ Rep1 Stages")+
  ylab("# of Insects in each stage")+xlab("Day")
```
##CO2 Production Over Time
````{r}
##Point Plot: Hourly CO2 production
dataCO2=data
dataCO2=subset(dataCO2,treat=="1"|treat=="2")
dataCO2=subset(dataCO2,day<=12)
dataCO2=subset(dataCO2,stage=="L")
dataCO2=subset(dataCO2,Tray!="12,23 1201-02"&Tray!="12,23 1201-01"&Tray!="16,23 1202"&Tray!="16,23 1201")
ggplot(data=dataCO2,aes(x=day,y=co2_hourly, color=treat))+
  facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  theme_classic()+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production")

##Point Plot: Hourly CO2 production
dataCO2=data
dataCO2=subset(dataCO2,treat=="3"|treat=="4")
dataCO2=subset(dataCO2,stage=="L")
ggplot(data=dataCO2,aes(x=day,y=co2_hourly, color=treat))+facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  theme_classic()+
  scale_colour_discrete(name="Treatment",breaks=c("3", "4"),labels=c("Diapause", "post45:Non-Diapause"))+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production")

##Point Plot: Hourly CO2 production by mass
dataCO2m=data
dataCO2m=subset(dataCO2m,treat=="1"|treat=="2")
dataCO2m=subset(dataCO2m,day<=12)
dataCO2m=subset(dataCO2m,stage=="L")
dataCO2m=subset(dataCO2m,Tray!="12,23 1201-02"&Tray!="12,23 1201-01"&Tray!="16,23 1202"&Tray!="16,23 1201")
ggplot(data=dataCO2m,aes(x=day,y=co2_hourly_mass, color=treat))+
  facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  theme_classic()+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production by Mass")

##Point Plot: Hourly CO2 production by mass
dataCO2m=data
dataCO2m=subset(dataCO2m,treat=="3"|treat=="4")
ggplot(data=dataCO2m,aes(x=day,y=co2_hourly_mass, color=treat))+facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  scale_colour_discrete(name="Treatment",breaks=c("3", "4"),labels=c("Diapause", "post 45:Non-Diapause"))+
  theme_classic()+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production by Mass")
````