---
title: "Respirometry Distributions"
editor_options: null
chunk_output_type: inline
output: html_document
df_print: paged
---
### Goal: Rear UZ and BE at 23C at 16:8 and 12:12 L:D regimens (UZ12, UZ16, BE12, BE16). Track CO2 production as a function of number of days after molting into the 5th instar. Track average weight gain as a function of number of days after molting into the 5th instar. Compare CO2 production and weight gain within strain and between L:D then compare L:D between strains 

##Call Data
````{r}
library(splines)
library(stats)
library(readxl)
library(ggplot2)
library(nlme)
library(lme4)
library(lmerTest)
library(ez)
library(lsr)
library(dplyr)
library(tidyr)
library(MASS)
library(doBy)
library(plyr)

#############--------------Read in the data-----------------######################
#PC
#setwd("/Users/jbrown/Documents/GitHub/Respirometry/Data")
#data=read_excel("Respir.xlsx")

#data=read_excel("/Users/JamesB/Google Drive/Graduate School/Self_JamesTBrown/GitHub/Rearing/Data/respir_pupa data.xlsx", sheet = "Sheet1")
str(data)
#data$treat<-as.factor(data$treatment)
#ggplot(data,aes(x=day,color=strain,fill=strain))+
#  geom_histogram()+
#  facet_grid(strain~treat)

#ggplot(data, aes(x=day))+
#  geom_density(alpha=.3)+
#  facet_wrap(treat~strain)+
#  ggtitle("Stages")

#MAC
data=read_excel("/Users/JamesB/Google Drive/Graduate School/Self_JamesTBrown/GitHub/Respirometry/Data/Respir.xlsx", sheet = "Sheet1")

############## Data Prep ###################
data=subset(data, VCO2!="NA") # Remove NAs from df
data=subset(data, syringe!="Blank Control") #Removing "Blank Control" syringes
data$syringe=as.character(data$syringe) #Set "syringe" as a character
data$strain<-as.factor(data$strain) #set strain as ind var
data$treat<-as.factor(data$treat) #set treat as factor as ind var
#data$day<-as.factor(data$day)
data$stage<-as.factor(data$stage)
#str(data)
````
## BE & UZ reps
```{r}
##BE Rep 1##
dataBEUZp=data
dataBEUZp=subset(dataBEUZp,stage=="L"|stage=="P")
dataBEUZp=subset(dataBEUZp, treat=="1"|treat=="2")
dataBEUZp=subset(dataBEUZp, Tray!="12,23 1201-01")
dataBEUZp=subset(dataBEUZp, Tray!="12,23 1201-02")
dataBEUZp=subset(dataBEUZp, Tray!="16,23 1202")
dataBEUZp=subset(dataBEUZp,Tray!="16,23 1201")
#dataBEr1p=subset(dataBEr1p, treat=="2")
#dataBEr1p=subset(dataBEUZp, day<=30)
#Stages: Change Over Time

dataBEUZp=subset(dataBEUZp,strain=="BE")
ggplot(dataBEUZp, aes(x=day, fill=stage))+
  geom_histogram(binwidth=.5, alpha=.5, position="dodge")+
  ggtitle("Stages")+
  scale_x_continuous(breaks=pretty(dataBEUZp$day, n=43))+ 
  facet_grid(treat~strain, scales ="free_y")+
  ylab("# of Insects in each stage")+xlab("Day")

ggplot(dataBEUZp, aes(x=day, fill=stage))+
  geom_density(alpha=.3)+   
  facet_grid(treat~strain, scales ="free_y")+
  ggtitle("Stages")

ggplot(data, aes(x=day, fill=stage))+
  geom_density(alpha=.3)+
  facet_wrap(~treat,scales="free_y")+
  ggtitle("Stages")
```
## comparison between definite diapausing BE's and the UZ's in diapause conditions
```{r}
dataBEpupa=subset(dataBEUZp,Tray=="12,23 0208")
dataBEpupa=subset(dataBEpupa,strain=="BE")
dataBEpupa=subset(dataBEpupa,syringe!="51")
dataBEpupa=subset(dataBEpupa,syringe!="56")
dataBEpupa=subset(dataBEpupa,syringe!="62")
dataBEpupa=subset(dataBEpupa,syringe!="64")
dataBEpupa=subset(dataBEpupa,syringe!="68")
dataBEpupa=subset(dataBEpupa,syringe!="69")
dataBEpupa=subset(dataBEpupa,syringe!="75")
dataBEpupa=subset(dataBEpupa,co2_hourly!="NA")
dataBEres=subset(dataBEUZp,Tray=="12,23 0208")
dataBEres=subset(dataBEres,syringe=="51"|syringe=="56"|syringe=="62"|syringe=="64"|syringe=="68"|syringe=="69"|syringe=="75")
dataBEUZres=dataBEUZp

diap_notprog=rbind(dataBEUZres,dataBEpupa)

ggplot(data=diap_notprog,aes(x=day,y=co2_hourly_mass,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(diap_notprog$day, n=30))+
  ggtitle("Change in CO2 x Mass Production Early Termination BE larvae")+
  ylab("CO2")+xlab("Day")

defdiap=rbind(dataBEres,dataBEUZres)

ggplot(data=defdiap,aes(x=day,y=co2_hourly_mass,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(defdiap$day, n=30))+
  ggtitle("Change in CO2 x Mass Production True Diapausing BE Larvae")+
  ylab("CO2")+xlab("Day")


ggplot(data=dataBEUZp,aes(x=day,y=co2_hourly_mass,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(defdiap$day, n=30))+
  ggtitle("Change in CO2 x Mass Production w/o Separation")+
  ylab("CO2")+xlab("Day")

#modnotrpog=lmer(co2_hourly_mass~strain*treat+(1|day),diap_notprog)
#moddefdiap=lmer(co2_hourly_mass~strain*treat+(1|day),defdiap)
#modall=lmer(co2_hourly_mass~strain*treat+(1|day),dataBEUZp)
#summary(modnotrpog)
#summary(moddefdiap)
#summary(modall)


```

##Dataframe Setup
````{r}
##########################################
#df BE Rep1 Stages Plots and Data Analysis
##########################################
dataBEr1s=data #subset of main df into BE rep1
dataBEr1s=subset(dataBEr1s, treat=="1" | treat=="2")
dataBEr1s=subset(dataBEr1s, Tray=="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")

##########################################
#df BE Rep2 Stages Plots and Data Analysis
##########################################
dataBEr2s=data #subset of main df into BE rep 2
dataBEr2s=subset(dataBEr2s, treat=="1" | treat=="2")
dataBEr2s=subset(dataBEr2s, Tray=="16,23 0208" | Tray=="12,23 0208")

##########################################
#df UZ Rep1 Stages Plots and Data Analysis
##########################################
dataUZr1s=data #subset of main df into UZ rep 1
dataUZr1s=subset(dataUZr1s, treat=="1" | treat=="2")
dataUZr1s=subset(dataUZr1s, Tray=="16,23 1228" | Tray=="12,23 1228")
```
## Treatment comparison of chainges in CO2 BE rep 2 and UZ rep 1 with analysis
```{r}
#Larva CO2: Change over time
dataBEUZ=subset(data, stage=="L")
dataBEUZ=subset(dataBEUZ,Tray!="12,23 1201-01")
dataBEUZ=subset(dataBEUZ,Tray!="12,23 1201-02")
dataBEUZ=subset(dataBEUZ,Tray!="16,23 1202")
dataBEUZ=subset(dataBEUZ,Tray!="16,23 1201")
dataBEUZ12=subset(dataBEUZ, treat=="1")
dataBEUZ16=subset(dataBEUZ, treat=="2")

dataBEUZf=subset(dataBEUZ,treat=="1"|treat=="2")
ggplot(data=dataBEUZf,aes(x=day,y=co2_hourly,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  scale_color_manual(values=c("1"="blue","2"="darkgreen"))+
  scale_x_continuous(breaks=pretty(dataBEUZf$day, n=30))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

ggplot(data=dataBEUZ12,aes(x=day,y=co2_hourly,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(dataBEUZ12$day, n=30))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

ggplot(data=dataBEUZ16,aes(x=day,y=co2_hourly,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(dataBEUZ16$day, n=10))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

data16be=subset(dataBEUZ16,strain=="BE")
data16be=subset(data16be,day=="4")
data16uz=subset(dataBEUZ16,strain=="UZ")
data16uz=subset(data16uz,day=="4")
treatpeaks16=rbind(data16be,data16uz)
#View(treatpeaks16)
modtreatpeaks16=lm(co2_hourly~strain,treatpeaks16)
summary(modtreatpeaks16)

databe=subset(dataBEUZ12,strain=="BE")
databe=subset(databe,day=="5")
datauz=subset(dataBEUZ12,strain=="UZ")
datauz=subset(datauz,day=="6")
treatpeaks=rbind(databe,datauz)
#View(treatpeaks)
modtreatpeaks=lm(co2_hourly~strain,treatpeaks)
summary(modtreatpeaks)

treatpeaks12and16=rbind(treatpeaks16,treatpeaks)
bothpeaks=lm(co2_hourly~treat,treatpeaks12and16)
summary(bothpeaks)

ggplot(treatpeaks12and16,aes(x=treat,y=co2_hourly,fill=strain))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual(values=c(UZ="purple",BE="orange"))+
  ggtitle("Day of Peak Metabolic Activity")+
  labs(y=expression(CO[2]*(mu*L/hr)),x="Strains")
```

## Treatment comparison of chainges in CO2 x Mass BE rep 2 and UZ rep 1 with analysis
```{r}
#Larva CO2 x Mass: Change over time
dataBEUZm=subset(data, stage=="L")
dataBEUZm=subset(dataBEUZm,Tray!="12,23 1201-01")
dataBEUZm=subset(dataBEUZm,Tray!="12,23 1201-02")
dataBEUZm=subset(dataBEUZm,Tray!="16,23 1202")
dataBEUZm=subset(dataBEUZm,Tray!="16,23 1201")
dataBEUZm12=subset(dataBEUZm, treat=="1")
dataBEUZm16=subset(dataBEUZm, treat=="2")

dataBEUZmf=subset(dataBEUZm,treat=="1"|treat=="2")
ggplot(data=dataBEUZmf,aes(x=day,y=co2_hourly_mass,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  scale_color_manual(values=c("1"="blue","2"="darkgreen"))+
  scale_x_continuous(breaks=pretty(dataBEUZmf$day, n=30))+
  ggtitle("Change in CO2 x Mass Production")+
  ylab("CO2 x Mass")+xlab("Day")

ggplot(data=dataBEUZm12,aes(x=day,y=co2_hourly_mass,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(dataBEUZm12$day, n=30))+
  ggtitle("Change in CO2 x Mass Production")+
  ylab("CO2 x Mass")+xlab("Day")

ggplot(data=dataBEUZm16,aes(x=day,y=co2_hourly_mass,group=strain,color=strain))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  scale_color_manual(values=c(UZ="purple",BE="orange"))+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(dataBEUZm16$day, n=10))+
  ggtitle("Change in CO2 x Mass Production")+
  ylab("CO2 x Mass")+xlab("Day")

datam16be=subset(dataBEUZm16,strain=="BE")
datam16be=subset(datam16be,day=="4")
datam16uz=subset(dataBEUZm16,strain=="UZ")
datam16uz=subset(datam16uz,day=="2")
treatmpeaks16=rbind(datam16be,datam16uz)
#View(treatmpeaks16)
modtreatmpeaks16=lm(co2_hourly_mass~strain,treatmpeaks16)
summary(modtreatmpeaks16)

datambe=subset(dataBEUZm12,strain=="BE")
datambe=subset(datambe,day=="1")
datamuz=subset(dataBEUZm12,strain=="UZ")
datamuz=subset(datamuz,day=="2")
treatmpeaks=rbind(datambe,datamuz)
#View(treatmpeaks)
modtreatmpeaks=lm(co2_hourly_mass~strain,treatmpeaks)
summary(modtreatmpeaks)

treatmpeaks12and16=rbind(treatmpeaks16,treatmpeaks)
bothmpeaks=lm(co2_hourly_mass~treat,treatmpeaks12and16)
summary(bothmpeaks)

ggplot(treatmpeaks12and16,aes(x=treat,y=co2_hourly_mass,fill=strain))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual(values=c(UZ="purple",BE="orange"))+
  ggtitle("Day of Peak Metabolic Activity Weighted by Wet Mass")+
  labs(y=expression(CO[2]*'/ Wet Mass' (mu*L/hr/g)),x="Strains")
```
## Treatment comparison of chainges in Mass BE rep 2 and UZ rep 1 with analysis
```{r}
#Larva Mass: Change over time
dataBEUZmass=subset(data, stage=="L"|stage!="P")
dataBEUZmass=subset(dataBEUZmass,Tray!="12,23 1201-01")
dataBEUZmass=subset(dataBEUZmass,Tray!="12,23 1201-02")
dataBEUZmass=subset(dataBEUZmass,Tray!="16,23 1202")
dataBEUZmass=subset(dataBEUZmass,Tray!="16,23 1201")
dataBEUZmass12=subset(dataBEUZmass, treat=="1")
dataBEUZmass16=subset(dataBEUZmass, treat=="2")
dataUZvUZ=subset(dataBEUZmass, strain=="UZ")
dataBEvBE=subset(dataBEUZmass, strain=="BE")

#View(dataBEvBE)

dataBEUZmass=subset(dataBEUZmass,treat=="1"|treat=="2")
ggplot(data=dataBEvBE,aes(x=day,y=co2_min_mass,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x  = element_text(vjust=0.5, size=16),axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))+
  scale_color_manual(values=c("1"="pink","2"="black"))+
  ggtitle("Change in CO2 Production Be")+
  ylab("Mass")+xlab("Day")

ggplot(data=dataUZvUZ,aes(x=day,y=co2_min_mass,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x  = element_text(vjust=0.5, size=16),axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))+
  scale_color_manual(values=c("1"="lightblue","2"="black"))+
  ggtitle("Change in CO2 Production UZ")+
  ylab("Mass")+xlab("Day")


ggplot(data=dataBEUZ16,aes(x=day,y=co2_min_mass,color=strain))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x = element_text(vjust=0.5, size=16),
        axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 10, by=2), limits=c(0,10))+
  scale_fill_manual(values=c("1"="lightblue","2"="black"))+
  ggtitle("Change in Mass Production")+
  ylab("co2")+xlab("Day")

  

ggplot(data=dataBEUZ12,aes(x=day,y=co2_min_mass,color=strain))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x = element_text(vjust=0.5, size=16),
        axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))+
  ggtitle("Change in CO2 Production Be")+
  ylab("co2")+xlab("Day")


ggplot(data=dataBEUZ16,aes(x=day,y=mass,color=strain))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x = element_text(vjust=0.5, size=16),
        axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 10, by=2), limits=c(0,10))+
  scale_fill_manual(values=c("1"="lightblue","2"="black"))+
  ggtitle("Change in Mass Production")+
  ylab("Mass")+xlab("Day")

  

ggplot(data=dataBEUZ12,aes(x=day,y=mass,color=strain))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05,size=1,shape=21) +
  theme(axis.text.x = element_text(vjust=0.5, size=16),
        axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))+
  ggtitle("Change in CO2 Production Be")+
  ylab("Mass")+xlab("Day")


datamass16be=subset(dataBEUZmass16,strain=="BE")
datamass16uz=subset(dataBEUZmass16,strain=="UZ")
datamass12uz=subset(dataBEUZmass12,strain=="UZ")
datamass12be=subset(dataBEUZmass12,strain=="BE")


datamass16uz=subset(dataBEUZmass16,strain=="UZ")
#datamass16uz=subset(datamass16uz,day=="6")
treatmasspeaks16=rbind(datamass16be,datamass16uz)
#View(treatmasspeaks16)
modtreatmasspeaks16=lm(mass~strain,treatmasspeaks16)
summary(modtreatmasspeaks16)

BE16UZ16wetmass=lm(mass~strain+day, data=dataBEUZ16)
summary(BE16UZ16wetmass)

datamassbe=subset(dataBEUZmass12,strain=="BE")
#datamassbe=subset(datamassbe,day=="10")
datamassuz=subset(dataBEUZmass12,strain=="UZ")
#datamassuz=subset(datamassuz,day=="10")
treatmasspeaks=rbind(datamassbe,datamassuz)
#View(treatmasspeaks)
modtreatmasspeaks=lm(mass~strain,treatmasspeaks)
summary(modtreatmasspeaks)

wetmasspeakBE16UZ16=aggregate(mass ~ strain+day, data = datamass16be, FUN = range ) 
dfBE16=merge(wetmasspeakBE16,datamass16be)
summary(dfBE16)
dfBE16=lm(mass~day,dfBE16)
summary(dfBE16)
wetmasspeakUZ16=aggregate(mass ~ syringe, data = datamass16uz, FUN = max ) 
dfUZ16=merge(wetmasspeakUZ16,datamass16uz)
summary(dfUZ16)
dfUZ16=lm(mass~day,dfUZ16)
summary(dfUZ16)
wetmasspeakBE12=aggregate(mass ~ syringe, data = datamass12be, FUN = max ) 
dfBE12=merge(wetmasspeakBE12,datamass12be)
summary(dfBE12)
dfBE12=lm(mass~day,dfBE12)
summary(dfBE12)
wetmasspeakUZ12=aggregate(mass ~ syringe, data = datamass12uz, FUN = max ) 
dfUZ12=merge(wetmasspeakUZ12,datamass12uz)
summary(dfUZ12)
dfUZ12=lm(mass~day,dfUZ12)
summary(dfUZ12)

ggplot(treatmasspeaks12and16,aes(x=treat,y=mass,fill=strain))+
  geom_boxplot()+
  theme_classic()+
  scale_fill_manual(values=c(UZ="purple",BE="orange"))+
  ggtitle("Day of Peak Mass")+
  ylab("Mass (g)")+
  xlab("Strains")

ggplot(treatmasspeaks12and16,aes(x=treat,y=co2_min_mass,fill=treat))+
  geom_boxplot()+
  theme_classic()+
  facet_wrap(~day)+
  scale_fill_manual(values=c(UZ="purple",BE="orange"))+
  ggtitle("CO2 production between treatmnets")+
  ylab("CO2 production")+
  xlab("Treatment")


treatmasspeaks12and16=rbind(treatmasspeaks16,treatmasspeaks)
BE16peaks=lm(mass~datamass16be$day,datamass16be)
summary(BE16peaks)
bothmasspeaks=lm(mass~treat,treatmasspeaks12and16)
summary(bothmasspeaks)


bothmasspeaks=lm(co2_min_mass~treat,treatmasspeaks12and16)
summary(bothmasspeaks)

uzcomp=rbind(datamassuz,datamass16uz)
uzpeak=lm(co2_min_mass~treat,uzcomp)
summary(uzpeak)

becomp=rbind(datamassbe,datamass16be)
bepeak=lm(co2_min_mass~treat,becomp)
summary(bepeak)

peak12=lm(co2_min_mass~strain,treatmasspeaks)
summary(peak12)

peak16=lm(co2_min_mass~strain,treatmasspeaks16)
summary(peak16)
```



```{r}
dataUZ12=subset(dataBEUZ12,strain=="UZ")
ggplot(data=dataUZ12,aes(x=day,y=co2_hourly,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  geom_vline(xintercept = 6)+
  scale_x_continuous(breaks=pretty(dataUZ12$day, n=30))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

dataBE12=subset(dataBEUZ12,strain=="BE")
ggplot(data=dataBE12,aes(x=day,y=co2_hourly,group=treat,fill=treat))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  geom_vline(xintercept = 5)+
  scale_x_continuous(breaks=pretty(dataBE12$day, n=30))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

dataUZ16=subset(dataBEUZ16,strain=="UZ")
ggplot(data=dataUZ16,aes(x=day,y=co2_hourly,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  geom_vline(xintercept = 4)+
  scale_x_continuous(breaks=pretty(dataUZ16$day, n=9))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

dataBE16=subset(dataBEUZ16,strain=="BE")
ggplot(data=dataBE16,aes(x=day,y=co2_hourly,group=treat,color=treat))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  geom_vline(xintercept = 4)+
  scale_x_continuous(breaks=pretty(dataBE16$day, n=9))+
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")
```

```{r}
###
# BE 12
####

dataBEmode2=subset(dataBEUZ,strain=="BE")
dataBEmode2=subset(dataBEmode2,treat=="1")
#dataBEmode2=subset(dataBEmode2,start=="20180224")
ggplot(data=dataBEmode2,aes(x=day,fill=start,color=start))+
  geom_density(alpha=.2,adjust=3)+
  facet_wrap(~start)+
  theme_classic()+
  geom_vline(xintercept = 6)+
  scale_x_continuous(breaks=pretty(dataBEmode2$day, n=50))+ 
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

getmode <- function(b) {
   uniqv <- unique(b)
   uniqv[which.max(tabulate(match(b, uniqv)))]
}
getmode <- function(u) {
   uniqv <- unique(u)
   uniqv[which.max(tabulate(match(u, uniqv)))]
}
b=c(dataBEmode2$co2_hourly)
resultb=getmode(b)
print(resultb)
u=c(dataBEmode2$day)
resultu=getmode(u)
print(resultu)

###
# BE 16 
####
dataBEmode3=subset(dataBEUZ,strain=="BE")
dataBEmode3=subset(dataBEmode3,treat=="2")
#dataBEmode3=subset(dataBEmode3,start=="20180224")
ggplot(data=dataBEmode3,aes(x=day,fill=start,color=start))+
  geom_density(alpha=.2,adjust=3)+
  facet_wrap(~start)+
  theme_classic()+
  geom_vline(xintercept = 4)+
  scale_x_continuous(breaks=pretty(dataBEmode3$day, n=8))+ 
  ggtitle("Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

getmode <- function(c) {
   uniqv <- unique(c)
   uniqv[which.max(tabulate(match(c, uniqv)))]
}
getmode <- function(d) {
   uniqv <- unique(d)
   uniqv[which.max(tabulate(match(d, uniqv)))]
}
e=c(dataBEmode3$co2_hourly)
resulte=getmode(e)
print(resulte)
d=c(dataBEmode3$day)
resultd=getmode(d)
print(resultd)

```

```{r}
#Larva CO2 by Mass: Change over time
dataBEUZ=subset(data, stage=="L")
dataBEUZ=subset(dataBEUZ,Tray!="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")
dataBEUZcm=subset(dataBEUZ, treat=="1"|treat=="2")

ggplot(data=dataBEUZcm,aes(x=day,y=co2_min_mass, color=treat,group=treat))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(~strain)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  scale_x_continuous(breaks=pretty(dataBEUZcm$day, n=20))+
  theme_bw()+
  ggtitle("Change in CO2 Production Weighted by Mass")+
  ylab("CO2 x Mass x Hour")+xlab("Day")



#diaBE=subset(dataBEUZ,day=="6")
#ndiaBE=subset(dataBE,day=="4")
#dataBE=rbind(diaBE,ndiaBE)
#dataBE=subset(dataBEUZcm,strain=="BE")
#dataBE=subset(dataBe,day<=10)
#modco2BE=lmer(co2_min_mass~treat + (1|day),data=dataBE)
#summary(modco2BE)

#diaUZ=subset(dataBEUZcm,day=="9")
#ndiaUZ=subset(dataBE,day=="5")
#dataUZ=rbind(diaUZ,ndiaUZ)
#dataUZ=subset(dataBEUZcm,strain=="UZ")
#dataUZ=subset(dataUZ,day<=10)
#modco2UZ=lmer(co2_min_mass~treat + (1|day),data=dataUZ)
#summary(modco2UZ)


#ggplot(data=dataNDia,aes(x=day,y=mass,group=strain,color=strain))+
  #stat_summary(fun.y=mean, geom="line",shape=18)+
  #stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  #scale_fill_manual(values=c(UZ="purple",BE="orange"))+
  #theme_bw()+
  #ggtitle("BE and UZ Non Diapause")+
  #ylab("Mass")+xlab("Day")
#modco2mnd=lmer(co2_hourly_mass~strain + (1|day),data=dataNDia)
#summary(modco2mnd)


#ggplot(data=dataNDia,aes(x=day,y=co2_min_mass,group=strain,color=strain))+
 # stat_summary(fun.y=mean, geom="line",shape=18)+
  #stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  #theme_bw()+
  #ggtitle("BE and UZ Non Diapause")+
  #ylab("CO2 x Min x Mass")+xlab("Day")




dataUZUZUZ=subset(data,strain=="UZ")
dataUZUZUZ=subset(dataUZUZUZ,treat=="1")
dataUZUZUZ$term="Deep Diapause"

dataBEpupa=subset(data,Tray=="12,23 0208")
dataBEpupa=subset(dataBEpupa,strain=="BE")
dataBEpupa=subset(dataBEpupa,syringe=="52"|syringe=="53"|syringe=="54"|syringe=="57"|syringe=="59"|syringe=="60"|syringe=="61"|syringe=="63"|syringe=="66"|syringe=="70"|syringe=="71"|syringe=="73"|syringe=="74")
dataBEpupa$term="Shallow Diapause"

dataBEres=subset(data,Tray=="12,23 0208")
dataBEres=subset(dataBEres,strain=="BE")
dataBEres=subset(dataBEres,syringe=="51"|syringe=="56"|syringe=="62"|syringe=="64"|syringe=="68"|syringe=="69"|syringe=="75")
dataBEres$term="Deep Diapause"

summary(dataBEpupa)
summary(dataBEres)
View(dataBEres)

mod12=lm(mass~day,dataBEpupa)

plot(mod12)
summary(mod12)



massdiff=rbind(dataBEpupa,dataBEres)
#massdiff=rbind(dataUZUZUZ,massdiff)
massdiff=subset(massdiff,co2_min_mass!="NA")
massdiff=subset(massdiff,day!="41")
massdiff=subset(massdiff,day!="43")
View(massdiff)

massdiff=subset(massdiff,day=="11")
modco2peakshallow=lm(mass~term,data=massdiff)
summary(massdiff)
summary(modco2peakshallow)


modaov12=aov(massdiff$mass~massdiff$term)
summary(modaov12)


ggplot(data=massdiff,aes(x=day,y=co2_min_mass,group=term,color=term))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar",width=0.65,size=1,shape=21) +
  scale_color_manual(values=c("Shallow Diapause" ="green", "Deep Diapause"="black"))+
  theme(axis.text.x  = element_text(vjust=0.5, size=16),axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))+
  labs(y=expression(CO[2]*'/ Production' (mu*L/g/min)),x="Days in 5th Instar")
  

ggplot(data=massdiff,aes(x=day,y=mass,group=term,color=term))+
  stat_summary(fun.y=mean, geom="line",shape=25,size=1)+
  stat_summary(fun.y=mean, geom="point",shape=19,size=2)+
  stat_summary(fun.data=mean_se, geom="errorbar",width=0.65,size=1,shape=21) +
  scale_color_manual(values=c("Shallow Diapause" ="blue", "Deep Diapause"="orange"))+
  theme(axis.text.x  = element_text(vjust=0.5, size=16),axis.text.y  = element_text(vjust=0.5, size=16))+
  scale_x_continuous(breaks = seq(0, 40, by=5), limits=c(0,40))

ggplot(data=massdiff,aes(x=day,y=co2_min_mass,group=term,color=term))+
  stat_summary(fun.y=mean, geom="line",shape=18)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_bw()+
  ggtitle("Shallow vs Deep Diapause")+
  ylab("CO2 x Min x Mass")+xlab("Day")




dataBEearly=subset(dataBEpupa,day=="6")
dataBElate=subset(dataBEres,day=="6")
dataUZlate=subset(dataUZUZUZ,day=="9")
Peakmass=rbind(dataBEearly,dataBElate)
Peakmass=rbind(Peakmass,dataUZlate)
Peakmass=subset(Peakmass,mass!="NA")
Peakmass$Tray=as.factor(Peakmass$Tray)
Peakmass$term=as.factor(Peakmass$term)
str(Peakmass)

modco2peakm=lm(co2_min_mass~term,data=massdiff)
summary(modco2peakm)


#Larva MASS: Change Over Time
#dataBEUZm=data
#dataBEUZm=subset(dataBEUZm, stage=="L")
#dataBEUZm=subset(dataBEUZm,Tray!="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")
#dataBEUZm=subset(dataBEUZm, treat=="1"|treat=="2")



#modq=aov(co2_min_mass~term,data=Peakmass)
#modq=aov(Peakmass, mass~term)
#summary(modq)

#plot(modq)

#massaov <- with(myData.mean,
#                  aov(stress ~ music * image +
#                     Error(PID / (music * image)))
#)


ggplot(data=dataBEpupa,aes(x=day,y=mass))+
  stat_summary(fun.y=mean, geom="line",shape=18)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_bw()+
  ggtitle("Early Terminators: Mass Peaks on Day 6")+
  ylab("Mass")+xlab("Day")

ggplot(data=dataBEpupa,aes(x=day,y=co2_min_mass))+
  stat_summary(fun.y=mean, geom="line")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_bw()+
  ggtitle("Early Terminators: Change in CO2 Production Weighted by Mass and Time")+
  ylab("CO2 x Min x Mass")+xlab("Day")

ggplot(data=dataBEres,aes(x=day,y=co2_min_mass))+
  stat_summary(fun.y=mean, geom="line",shape=18)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_bw()+
  ggtitle("Late Terminators: Mass Peaks on Day 8")+
  ylab("CO2 x Min x Mass")+xlab("Day")

ggplot(data=dataBEres,aes(x=day,y=mass))+
  stat_summary(fun.y=mean, geom="line",shape=18)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_bw()+
  ggtitle("Late Terminators: Mass Peaks on Day 8")+
  ylab("Mass")+xlab("Day")

dataUZUZ=subset(dataBEUZcm,strain=="UZ")
dataUZUZ=subset(dataUZUZ,treat=="1")
ggplot(data=dataBEUZcm,aes(x=day,y=co2_min_mass))+
  stat_summary(fun.y=mean, geom="line")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  scale_x_continuous(breaks=pretty(dataBE12$day, n=30))+
  theme_bw()+
  ggtitle("UZ12: Change in CO2 Production Weighted by Mass and Time")+
  ylab("CO2 x Min x Mass")+xlab("Day")

ggplot(data=dataBEUZcm,aes(x=day,y=mass))+
  stat_summary(fun.y=mean, geom="line")+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  scale_x_continuous(breaks=pretty(dataBE12$day, n=30))+
  theme()+
  ggtitle("UZ12: Mass Peak on Day 10")+
  ylab("Mass")+xlab("Day")
```

```{r}
###
#dataBEUZm=subset(data, stage=="L")
#dataBEUZm=subset(dataBEUZm,Tray!="12,23 1201-01"|Tray=="12,23 1201-02"|Tray=="16,23 1202"|Tray=="16,23 1201")
#dataBEUZm=subset(dataBEUZm,day<=9)
#dataBEUZm=subset(dataBEUZm, treat=="1"|treat=="2")
ggplot(data=dataBEUZm,aes(x=day,y=mass, color=strain,group=strain))+
  stat_summary(fun.y=mean, geom="line")+
  facet_grid(strain~treat)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.05) +
  theme_classic()+
  ylab("Mass")+xlab("Day")

ggplot(data=dataBEUZm,aes(x=day,y=mass))+
  geom_smooth()+
  facet_wrap(~treat)+
  geom_point()+
  theme_classic()+
  ggtitle("Change in  Mass")+
  ylab("Mass")+xlab("Day")

dataBE=subset(dataBEUZm,strain=="BE")
#dataBE=subset(dataBe,day<=10)
modco2m=lmer(mass~treat + (1|day),data=dataBE)
summary(modco2m)

dataUZ=subset(dataBEUZm,strain=="UZ")
#dataUZ=subset(dataUZ,day<=10)
modco2m=lmer(mass~treat + (1|day),data=dataUZ)
summary(modco2m)

dataDia=subset(dataBEUZm,treat=="1")
#dataBE=subset(dataBe,day<=10)
modco2md=lmer(mass~strain + (1|day),data=dataDia)
summary(modco2md)

dataNDia=subset(dataBEUZm,treat=="2")
#dataUZ=subset(dataUZ,day<=10)
modco2mnd=lmer(mass~strain + (1|day),data=dataNDia)
summary(modco2mnd)
###


ggplot(dataBEUZm, aes(x=day,color=mass))+
  geom_histogram(aes(fill=treat),alpha=.3)+
  facet_grid(treat~strain, scales ="free_y")+
  scale_x_continuous(breaks=pretty(dataBEUZm$day, n=25))+ 
  ggtitle("Mass")

ggplot(dataBEUZm, aes(x=day,color=mass))+
  geom_density(aes(fill=treat),alpha=.3)+
  facet_wrap(~treat)+
  scale_x_continuous(breaks=pretty(dataBEUZm$day, n=25))+ 
  ggtitle("Mass")
```

```

##BE Rep 1: Changes in CO2, CO2 Weighted by Mass, Mass, and Stage, across time
```{r} 

##################
#### BE REP 1 ####
##################

#Larva CO2: Change over time
dataBEr1co2=subset(dataBEr1s, stage=="L")
ggplot(data=dataBEr1co2,aes(x=day,y=co2_hourly))+
  geom_smooth()+
  facet_grid(treat~start, scales ="free_y")+
  geom_point()+
  theme_classic()+
  ggtitle("BE Rep1 Change in CO2 Production")+
  ylab("CO2")+xlab("Day")

#Larva CO2 by Mass: Change over time
dataBEr1co2m=subset(dataBEr1s, stage=="L")
ggplot(data=dataBEr1co2m,aes(x=day,y=co2_hourly_mass))+
  geom_smooth()+
  facet_grid(treat~start, scales ="free_y")+
  geom_point()+
  theme_classic()+
  ggtitle("BE Rep1 Change in CO2 Production Weighted by Mass")+
  ylab("CO2 x Mass")+xlab("Day")

#Larva MASS: Change Over Time
dataBEr1m=dataBEr1s
dataBEr1m=subset(dataBEr1m, stage=="L")
ggplot(data=dataBEr1m,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  facet_grid(treat~start, scales ="free_y")+
  stat_peaks(geom = "text") +
  facet_wrap(~syringe)+
  theme_minimal()+
  ggtitle("BE Rep1 Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")

ggplot(dataBEr1m, aes(x=day,color=mass))+
  geom_density(aes(fill=treat),alpha=.3)+
  facet_grid(treat~start, scales ="free_y")+
  scale_x_continuous(breaks=pretty(dataBEr1m$day, n=25))+ 
  ggtitle("BE Rep1 Mass")

##BE Rep 1##
dataBEr1p=subset(dataBEr1s,stage=="L"|stage=="P")
#dataBEr1p=subset(dataBEr1p, treat=="2")
dataBEr1p=subset(dataBEr1p, day<=30)
#Stages: Change Over Time

ggplot(dataBEr1p, aes(x=day, fill=stage))+
  theme_classic()+
  geom_histogram(binwidth=.5, alpha=.5, position="identity")+
  scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,13,15,17))+
  ggtitle("BE Rep1 Stages")+
  ylab("# of Insects in each stage")+xlab("Day")

ggplot(dataBEr1p, aes(x=day, fill=stage))+
  geom_density(alpha=.3)+   
  facet_grid(treat~start, scales ="free_y")+
  ggtitle("BE Rep1 Stages")
```

##BE Rep1 Stats
```{r}
##############################################
###### BE Rep 1 Peak Mass Comaprison #########
##############################################

#fit first degree polynomial equation:
fit  <- lm(mass~day, data = dataBEr1m)
summary(fit)
coef(fit)

#second degree
fit2 <- lm(mass~poly(day,2,raw=TRUE), data = dataBEr1m)
summary(fit2)
coef(fit2)

#third degree
fit3 <- lm(mass~poly(day,3,raw=TRUE), data = dataBEr1m)
summary(fit3)
coef(fit3)

#fourth degree
fit4 <- lm(mass~poly(day,4,raw=TRUE), data = dataBEr1m)
summary(fit4)
coef(fit4)

anova(fit,fit2) #fit2
anova(fit,fit3) #fit3
anova(fit,fit4) #fit4 
anova(fit2,fit3) #fit3
anova(fit2,fit4) #fit4
anova(fit3,fit4) #fit4
```
##BE Rep 2: Changes in CO2, CO2 Weighted by Mass, Mass, and Stage, across time
```{r}
##################
#### BE REP 2 ####
##################
#Larva CO2: Change over time
dataBEr2co2=subset(dataBEr2s, stage=="L")
ggplot(data=dataBEr2co2,aes(x=day,y=co2_hourly))+
  geom_smooth()+
  facet_grid(treat~start, scales ="free_y")+
  geom_point()+
  theme_classic()+
  ggtitle("BE Rep2 Change in CO2 Production")+
  ylab("CO2")+xlab("Day")


#Larva CO2 by Mass: Change over time
dataBEr2co2m=subset(dataBEr2s, stage=="L")
ggplot(data=dataBEr2co2m,aes(x=day,y=co2_hourly_mass))+
  geom_smooth()+
  facet_grid(treat~start, scales ="free_y")+
  geom_point()+
  theme_classic()+
  ggtitle("BE Rep2 Change in CO2 Production Weighted by Mass")+
  ylab("CO2 x Mass")+xlab("Day")


#Larva MASS: Change Over Time
dataBEr2m=dataBEr2s
dataBEr2m=subset(dataBEr2m, stage=="L")
ggplot(data=dataBEr2m,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  facet_grid(treat~start, scales ="free_y")+
  geom_smooth()+
  theme_classic()+
  ggtitle("BE Rep2 Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")

ggplot(dataBEr2m, aes(x=day,color=mass))+
  geom_density(aes(fill=treat),alpha=.3)+
  facet_grid(treat~start, scales ="free_y")+
  scale_x_continuous(breaks=pretty(dataBEr2m$day, n=25))+ 
  ggtitle("BE Non Diapause Rep1 Stages")

##BE Rep 2##
dataBEr2p=subset(dataBEr2s,stage=="L"|stage=="P")
#dataBEr2p=subset(dataBEr2p, treat=="2")
dataBEr2p=subset(dataBEr2p, day<=20)
#Stages: Change Over Time

ggplot(dataBEr2p, aes(x=day, fill=stage))+
  geom_density(alpha=.3)+
  facet_wrap(~treat, scales ="free_y")+
  ggtitle("BE Non Diapause Rep2 Stages")

```
##UZ Rep 1: Changes in CO2, CO2 Weighted by Mass, Mass, and Stage, across time
```{r}
##################
#### UZ REP 1 ####
##################

#Larva CO2: Change over time
dataUZr1co2=subset(dataUZr1s, stage=="L")
ggplot(data=dataUZr1co2,aes(x=day,y=co2_hourly))+
  geom_smooth()+
  facet_grid(treat~start, scales ="free_y")+
  geom_point()+
  theme_classic()+
  ggtitle("UZ Rep1 Change in CO2 Production")+
  ylab("CO2")+xlab("Day")


#Larva CO2 by Mass: Change over time
dataUZr1co2m=subset(dataUZr1s, stage=="L")
ggplot(data=dataUZr1co2m,aes(x=day,y=co2_hourly_mass))+
  geom_smooth()+
  facet_grid(treat~start)+
  geom_point()+
  theme_classic()+
  ggtitle("UZ Rep1 Change in CO2 Production Weighted by Mass")+
  ylab("CO2 x Mass")+xlab("Day")


#Larva MASS: Change Over Time
dataUZr1m=dataUZr1s
dataUZr1m=subset(dataUZr1m, stage=="L")
ggplot(data=dataUZr1m,aes(x=day,y=mass))+
  geom_line(aes(group=syringe,color=syringe))+
  facet_grid(treat~start, scales ="free_y")+
  geom_smooth()+
  theme_classic()+
  ggtitle("UZ Rep1 Larvae Mass Increase")+
  ylab("Mass")+xlab("Day")

ggplot(dataUZr1m, aes(x=day,color=mass))+
  geom_density(aes(fill=treat),alpha=.3)+
  facet_grid(treat~start, scales ="free_y")+
  scale_x_continuous(breaks=pretty(dataUZr1m$day, n=25))+ 
  ggtitle("UZ Rep1 Stages")



##UZ Rep 1##
dataUZr1p=subset(dataUZr1s,stage=="L"|stage=="P")
#dataUZr1p=subset(dataUZr1p, treat=="2")
dataUZr1p=subset(dataUZr1p, day<=20)
#Stages: Change Over Time

ggplot(dataUZr1p, aes(x=day, fill=stage))+
  geom_density(alpha=.3)+
  facet_grid(treat~start, scales ="free_y")+
  ggtitle("UZ Rep1 Stages")

ggplot(dataUZr1p, aes(x=day, fill=stage))+
  theme_classic()+
  geom_histogram(binwidth=.5, alpha=.5, position="identity")+
  scale_x_discrete(limits=c(1,2,3,4,5,6,7,8,9,10,11,13,15,17))+
  ggtitle("UZ Non Diapause Rep1 Stages")+
  ylab("# of Insects in each stage")+xlab("Day")
```


##CO2 Production Over Time
````{r}
##Point Plot: Hourly CO2 production
dataCO2=data
dataCO2=subset(dataCO2,treat=="1"|treat=="2")
dataCO2=subset(dataCO2,day<=12)
dataCO2=subset(dataCO2,stage=="L")
dataCO2=subset(dataCO2,Tray!="12,23 1201-02"&Tray!="12,23 1201-01"&Tray!="16,23 1202"&Tray!="16,23 1201")
ggplot(data=dataCO2,aes(x=day,y=co2_hourly, color=treat))+
  facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  theme_classic()+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production")

##Point Plot: Hourly CO2 production
dataCO2=data
dataCO2=subset(dataCO2,treat=="3"|treat=="4")
dataCO2=subset(dataCO2,stage=="L")
ggplot(data=dataCO2,aes(x=day,y=co2_hourly, color=treat))+facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  theme_classic()+
  scale_colour_discrete(name="Treatment",breaks=c("3", "4"),labels=c("Diapause", "post45:Non-Diapause"))+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production")

##Point Plot: Hourly CO2 production by mass
dataCO2m=data
dataCO2m=subset(dataCO2m,treat=="1"|treat=="2")
dataCO2m=subset(dataCO2m,day<=12)
dataCO2m=subset(dataCO2m,stage=="L")
dataCO2m=subset(dataCO2m,Tray!="12,23 1201-02"&Tray!="12,23 1201-01"&Tray!="16,23 1202"&Tray!="16,23 1201")
ggplot(data=dataCO2m,aes(x=day,y=co2_hourly_mass, color=treat))+
  facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  scale_colour_discrete(name="Treatment",breaks=c("1", "2"),labels=c("Diapause", "Non-Diapause"))+
  theme_classic()+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production by Mass")

##Point Plot: Hourly CO2 production by mass
dataCO2m=data
dataCO2m=subset(dataCO2m,treat=="3"|treat=="4")
ggplot(data=dataCO2m,aes(x=day,y=co2_hourly_mass, color=treat))+facet_wrap(~strain)+
  geom_point()+
  geom_smooth(method="loess")+
  scale_colour_discrete(name="Treatment",breaks=c("3", "4"),labels=c("Diapause", "post 45:Non-Diapause"))+
  theme_classic()+
  ggtitle("Larvae CO2 production")+
  ylab("CO2 production by Mass")
````